---
title: "BAN430 Mandatory Assignment"
format: html
editor: visual
---

## Libraries

Please make sure to have the following packages installed before running the code. The code does not automatically check if libraries are missing, nor installs the packages automatically.

```{r, eval=T, error=TRUE, message=FALSE, warning=FALSE}
library(fpp3)
library(fable)
library(tidyverse)
library(lubridate)
library(urca)
library(scales)
```

On this assignment, we work with weekly sales data from 45 Walmart stores between 2010 and 1013. We load the data from the course github page:

```{r, eval=T, error=TRUE, message=FALSE, warning=FALSE}
# Load and transform data to tsibble
walmart <- readr::read_csv("https://raw.githubusercontent.com/holleland/BAN430/master/data/Walmart.csv") %>% 
  mutate(Date = yearweek(as.Date(Date, format = "%d-%m-%Y"))) %>% 
  rename(Yearweek = Date) %>% 
  as_tsibble(index = Yearweek,
             key = Store)
```

# TASK 2: Preliminary Data Analysis

First, we do some preliminary data analysis to determine whether there is any seasonal pattern or trend present, or whether any of the other variables have a visual effect on weekly sales.

```{r, eval=T, error=TRUE, message=FALSE, warning=FALSE}
# Time series plot of the weekly sales data
walmart %>% autoplot(Weekly_Sales) +
  theme_minimal() +
  theme(legend.position = "none") +
  labs(title = "Weekly sales of 45 Walmart stores") +
  scale_y_continuous(labels = label_number()) +
  xlab("Week") + ylab("weekly sales in USD")

# aggregate the data from weekly to monthly (mean) sales
walmart.month <- walmart %>% 
  group_by(Store) %>% 
  index_by(Month =~yearmonth(.)) %>% 
  summarize(Mean_Monthly_Sales = mean(Weekly_Sales))

# mean Sales per month for all stores
walmart.month %>% autoplot() +
  scale_y_continuous(labels = label_number()) +
  theme(legend.position = "none")
```
